{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-04 Paper/main.tex
Cleaned up bibliography

	\begin{figure}[H]
		\begin{center}
			\includegraphics[width = \textwidth]{../Graphics/FinderSD.jpg}
			\caption{Finder SD - A Near-Infrared-Spectroscope built by HiperScan GmbH \\
			(source: https://www.hiperscan.com/files/apoident/uploads/Bilder/Neue\_Website/Produkte/FinderSD.jpg)}
		\end{center}
	\end{figure}

>>>>

	\begin{figure}[H]
		\begin{center}
			\includegraphics[width = \textwidth]{../Graphics/FinderSD.jpg}
			\caption{Finder SD - A Near-Infrared-Spectroscope built by HiperScan GmbH \\
			(Source: https://www.hiperscan.com/files/apoident/uploads/Bilder/Neue\_Website/Produkte/FinderSD.jpg)}
		\end{center}
	\end{figure}
